\section{Coaching}
This chapter we will discuss the meeting with the coach.

\subsection{Coaching 1}
This meeting was held on the 10th of September 2018. We introduced ourselves to each other. This was done in less than 5 minutes because we were in the same class throughout the first half of the first year.

\subsection{Coaching 2}
This meeting was held on the 2th of November 2018. During this meeting we discussed the draft of the team manifesto. We integrated our two personal learning goals from Project Agile Development into the manifesto. The coach told us more about the two competences that were at the center of this project, Ethics and Research.

\subsection{Coaching 3}
This meeting was held on the 28th of November 2018. During the previous meeting the coach asked us to look back at the previous projects and take note of our own behavior and the effect of this behavior on the team members and the end result. This information is labeled as classified and won't be publicly published.

\subsection{Coaching 4}
This meeting was held on the 5th of December 2018. We discussed the feedback forms that each of us had filled in for each of the team members. After discussing them we all thought of two SMART learning goals based on the feedback from our team members. We also discussed the status and planning of the project. We were way ahead of the schedule and were researching possible autonomous behavior of the Rover.

\subsection{Coaching 5}
This meeting was held on the 12th of December 2018. We discussed the retrospective of the previous sprints with the coach. We also discussed our portfolio and talked about the internship.

\subsection{Coaching 6}
TBD
