\section{Collaboration}

\subsection{Missionstatement}
This project we want to build a robot that is able to detect people in the rubble of buildings. It needs to be deployable in disaster regions. We will receive a robot from our instance to use for our project, we will need to be able to control the robot from our mobile device.

\subsection{Objective}
At the end of this project we want to produce a working robot and we would like to see the thing we can accomplish as a team of only TI students. We want to learn different things with this project, things like; controlling a robot with code, understanding how the hardware of a robot works, making an app, knowing how to connect a robot to a phone with Bluetooth and we hope to learn more about scrum. Our goal is also to accomplish all our learning goals.

\subsection{Agreements and expectations}
\begin{itemize}
	\item Every member of the team is present at meetings of the group
	\item If a member can’t be present at a meeting of the group, he has reported this to the other members of the group by WhatsApp or email.
	\item Every member is accessible through WhatsApp or email
	\item WhatsApp is used for general communication (not for personal communication)
	\item Git is used for storage and management of versions
	\item ZenHub is used for management of board to implement Scrum
	\item If something isn’t clear to you, you tell this to the other members of the team, so that the other members can help you.
	\item You are responsible for your own work and for having your stuff with you.
	\item Decisions are made with all the members of the team, not individual.
	\item Everyone does everything they can to produce a good-looking end product...
\end{itemize}

\subsection{Agreements for team blog}
On the blog you can find weekly updates of our product, which problems we have faced in the past week and how we managed to solve them. If something interesting happens, we will put it on the blog too. Each team member is responsible for the blog. A team member should update/create the blog post of the week with the work that he or she has done. 

